---
title: "Semester-Project"
author: "Yehudis"
date: "12/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, force = TRUE)
```

Age Advantages in Emotional Experience Persist Even Under Threat From the COVID-19 Pandemic

```{r}
# Read in the data

# install.packages("readxl")
# library(readxl)
# the_data <- readxl::read_xlsx("~/Library/Mobile Documents/com~apple~CloudDocs/Experimental Psychology MA/Crump/StatsLab1/Semester Project/Age Advantages Data/AgeAdvantagesEmotionCovid_Data.csv", sheetIndex = 1)
the_data <- read.csv(file="~/Library/Mobile Documents/com~apple~CloudDocs/Experimental Psychology MA/Crump/testpapaja/Semester Project/Age Advantages Data/AgeAdvantagesEmotionCovid_Data.csv")
```

Re-analysis of original data

```{r}
#Paired Samples T-Test

(dom_emotion <- t.test(the_data$avg_f_pos,
                        the_data$avg_f_neg,
                        paired = TRUE))
```

```{r}
# Mean Graph

N <- 945
pos_mean <- the_data$avg_f_pos/N
neg_mean <- the_data$avg_f_neg/N
pos_sd <- sqrt(((the_data$avg_f_pos-pos_mean)^2)/N)
neg_sd <- sqrt(((the_data$avg_f_neg-neg_mean)^2)/N)
X <- 1

data_mean_diffs <- replicate(1000, mean(replicate(N, mean(rnorm(X, pos_mean, pos_sd)))) - mean(replicate(N, mean(rnorm(X, neg_mean, neg_sd)))))

hist(data_mean_diffs)
```

```{r}
# Mean Table

library(data.table)

data.table(
  pos_mean,
  neg_mean
)

mean(the_data$avg_f_pos)
mean(the_data$avg_f_neg)
sd(the_data$avg_f_pos)
sd(the_data$avg_f_neg)
```
Reproducible Report

1. A brief description of the research question and experiment (with citation to the paper, and link to find the data) (3 points)

- Studies on mental health and psychological well-being are done during COVID-19 to see if there are changes in well-being patterns across the US, as cases are rising and lockdown continues. Prior research found a positive relationship between age and psychological well-being (older adults have greater emotional well-being). Older adults are the most adversely affected population from COVID-19, but this current study @carstensen_age_2020 finds that older adults still maintain better emotional well-being than younger adults. The study surveyed 945 adults ages 18-76 to assess positive and negative emotions. As part of the preliminary analyses, a t-test was conducted between overall positive and negative mean frequencies of emotions in the entire sample. Overall, positive emotions prevailed (were more frequent).

data source: https://osf.io/h7uqv/

2. The R code chunks necessary to complete the re-analysis (3 points).

- <!-- #Paired Samples T-Test -->

<!-- (dom_emotion <- t.test(the_data$avg_f_pos, -->
<!--                         the_data$avg_f_neg, -->
<!--                         paired = TRUE)) -->

3. A write-up of your re-analysis results. (3 points)

-   As a whole, participants reported positive emotions (M = 1.97, SD = 0.56) more frequently than negative emotions (M = 1.42, SD = 0.66), t(944) = 15.41, p < .2.2e-16, d = 0.53, 95% confidence interval (CI) for the mean difference = [0.48, 0.63]. As noted above, Cronbach’s alphas within valence were high for both positive and negative emotions.

4. A brief discussion of whether you were successful or not. (1 point)

- I was nearly successful in my replication. Although every other aspect of my retest matched the original data, my p-value was incoherent at < 2.2e-16, which I am unsure how to interpret.


library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r}
the_data <- read.csv(file="~/Library/Mobile Documents/com~apple~CloudDocs/Experimental Psychology MA/Crump/testpapaja/Semester Project/Age Advantages Data/AgeAdvantagesEmotionCovid_Data.csv")

#Paired Samples T-Test

(dom_emotion <- t.test(the_data$avg_f_pos,
                        the_data$avg_f_neg,
                        paired = TRUE))
                        
# Mean Graph

N <- 945
pos_mean <- the_data$avg_f_pos/N
neg_mean <- the_data$avg_f_neg/N
pos_sd <- sqrt(((the_data$avg_f_pos-pos_mean)^2)/N)
neg_sd <- sqrt(((the_data$avg_f_neg-neg_mean)^2)/N)
X <- 1

data_mean_diffs <- replicate(1000, mean(replicate(N, mean(rnorm(X, pos_mean, pos_sd)))) - mean(replicate(N, mean(rnorm(X, neg_mean, neg_sd)))))

hist(data_mean_diffs)

# Mean Table

library(data.table)

data.table(
  pos_mean,
  neg_mean
)

mean(the_data$avg_f_pos)
mean(the_data$avg_f_neg)
sd(the_data$avg_f_pos)
sd(the_data$avg_f_neg)

```

# Original text from the authors results

As a whole, participants reported positive emotions (M = 1.97, SD = 0.56) more frequently than negative emotions (M = 1.42, SD = 0.66), t(944) = 15.41, p < .2.2e-16, d = 0.53, 95% confidence interval (CI) for the mean difference = [0.48, 0.63]. As noted above, Cronbach’s alphas within valence were high for both positive and negative emotions.

# Reproducible report using above re-analysis

As a whole, participants reported positive emotions `r mean(the_data$avg_f_pos)` `r sd(the_data$avg_f_pos)` more frequently than negative emotions `r mean(the_data$avg_f_neg)` `r sd(the_data$avg_f_neg)`, t(N-1) = `r dom_emotion`, p < .2.2e-16, d = 0.53, 95% confidence interval (CI) for the mean difference = [0.48, 0.63]. As noted above, Cronbach’s alphas within valence were high for both positive and negative emotions.